\section*{Data Management Plan}

% Plans for data management and sharing of the products of
% research. Proposals must include a supplementary document of no more
% than two pages labeled “Data Management Plan”. This supplement should
% describe how the proposal will conform to NSF policy on the dissemination
% and sharing of research results (see AAG Chapter VI.D.4), and may include:
%
% - the types of data, samples, physical collections, software,
%   curriculum materials, and other materials to be produced in the course
%   of the project;
%
% - the standards to be used for data and metadata format and content
%   (where existing standards are absent or deemed inadequate, this should
%   be documented along with any proposed solutions or remedies);
%
% - policies for access and sharing including provisions for appropriate
%   protection of privacy, confidentiality, security, intellectual property,
%   or other rights or requirements;
%
% - policies and provisions for re-use, re-distribution, and the
%   production of derivatives; and
%
% - plans for archiving data, samples, and other research products,
%   and for preservation of access to them.

%\todo{go over Xi's version}

%
The goal of this project is to explore systems techniques for constructing web
services that are privacy-compliant by construction.
%
As part of this effort, we plan to build working prototypes of web services and
the systems that back them, including a new database, a blob store, and modified
RPC libraries as well as plugins for existing systems (\eg ML frameworks).
%
All source code, configuration files, and instructions for reproducing published
measurements of our systems will be made public, hosted via GitHub version
control and accessible from the project website at Brown University.
%
The data generated through the work described in this proposal will consist of
papers, source code,  benchmarks, and experimental results.
%

%
The PI brings extensive experience with building and contributing to open-source
software.
%
Prior systems of his have become popular open-source projects (\eg the Noria
dataflow system, which has 21 contributors, 102 pull requests, and 2,600 stars
on GitHub), or have been integrated with popular open-source software (\eg the
Firmament cluster scheduler, for which an open-source community developed a
plugin for Google's Kubernetes cluster manager).
%
All of this software is available for public access on GitHub.
%

\paragraph{Policies for Data Access and Sharing.}
We will make the source code for our new dataflow systems, the federated
database, the RPC library patches and inter-system dataflow tracking, and
the tools for specifying, enforcing, and checking user-specific privacy
policies, available for public download under open-source licenses.
%
To ensure broad impact of our work, the source code will be available for reuse
without restriction.
%

\paragraph{Reproducibility of Experimental Results}
%
We will publish our results in peer-reviewed systems venues such as SOSP and
OSDI, or database venues such as SIGMOD and VLDB.
%
When a venue has a pre-publiction artifact evaluation process, we will
participate and support third-party reproduction of our results.
%

\paragraph{Data Formats.}
All data generated will be labeled and stored in digital formats, and we will
ensure that any empirical data produced in our experiments and our source code
distributions use standard formats.
%
For papers, we will keep both a PDF copy of the document and the {\LaTeX}
source.
%
Experimental results will be stored in standard formats compatible with
widely-used software tools, such as spreadsheets or ASCII text files.
%
We will also include sufficient documentation with our released code and data
to allow third parties to reconstruct our published results.
%

\paragraph{Data Retention.}
Data will be retained for at least three years beyond the award period, as
required by NSF guidelines.
%
The GitHub version control repositories will ensure the integrity of data and
allow for long-term retention.
%

\paragraph{Data Privacy.}
This research project does not involve confidential data or source code.

%\paragraph{Responsible data management.}
%All members of the investigative team with data access will be
%instructed and certified in responsible research and scholarship
%(e.g., via the Responsible Conduct of Research
%course provided by the MIT Office of Sponsored Projects).  All data
%acquired and preserved in the context of this proposal will be further
%governed by the policies of the Massachusetts Institute of Technology
%pertaining to intellectual property, record
%retention, and data management.

